Reanalysis Step 4: Propensity Score Analysis with Twang

### 2025-09-03 reanalysis-4-propensity_scores.qmd
cache ps score

# CACHING CONFIGURATION
use_cache <- FALSE  # Set to FALSE to force re-computation
cache_dir <- file.path(reanalysis_data_dir, "ps_cache")
if (!dir.exists(cache_dir)) {
  dir.create(cache_dir, recursive = TRUE)
}

@@

# Function to process a single imputation
process_imputation <- function(i, imp_datasets, formula, trees, cache_path, use_caching, worker_id, log_dir) {
  # Recreate variables inside function to avoid scoping issues
  library(twang)

@@

  if (use_caching && file.exists(cache_file)) {
    cached_result <- readRDS(cache_file)
    weights <- cached_result$weights

    # Log cache hit
    cache_msg <- paste0("[Worker ", worker_id, "] Imputation ", i, " loaded from cache")
    cat(paste0(Sys.time(), " - ", cache_msg, "\n"), file = worker_log_file, append = TRUE)

@@

# Process each imputation sequentially
sequential_results <- lapply(
  1:n_imputations,
  function(i) {
    worker_id <- 1  # Single worker for sequential processing
    process_imputation(i, imputed_datasets, ps_formula, n_trees, cache_dir, use_cache, worker_id, log_dir)
  }
)

@@

  # Log individual result summary in main log
  if (res$cached) {
    log_message(paste0("Imputation ", res$imputation, " (Worker ", res$worker_id, "): Loaded from cache"))
  } else {
    log_message(paste0("Imputation ", res$imputation, " (Worker ", res$worker_id, "): Fitted in ", res$time_mins, " minutes"))
  }
}

@@

>>>>

# CACHING CONFIGURATION
use_cache <- TRUE  # Set to TRUE to use cache, FALSE to force re-computation
cache_max_age_days <- 2  # Cache files older than this many days will be recomputed
cache_dir <- file.path(reanalysis_data_dir, "ps_cache")
if (!dir.exists(cache_dir)) {
  dir.create(cache_dir, recursive = TRUE)
}

# Get list of existing cache files with their modification times
if (use_cache) {
  cache_files <- list.files(cache_dir, pattern = "^twang_imp_.*\\.rds$", full.names = TRUE)
  if (length(cache_files) > 0) {
    cache_info <- file.info(cache_files)
    cache_info$file <- basename(rownames(cache_info))
    cache_info$age_days <- as.numeric(difftime(Sys.time(), cache_info$mtime, units = "days"))
    log_message(paste0("Found ", nrow(cache_info), " cached files in ", cache_dir))
    log_message(paste0("Cache staleness threshold: ", cache_max_age_days, " days"))
  } else {
    cache_info <- NULL
    log_message("No cached files found")
  }
} else {
  log_message("Cache disabled - will recompute all imputations")
}

@@

# Function to process a single imputation
process_imputation <- function(i, imp_datasets, formula, trees, cache_path, use_caching, worker_id, log_dir, cache_max_age_days) {
  # Recreate variables inside function to avoid scoping issues
  library(twang)

@@

  # Determine if we should use cached file
  should_use_cache <- FALSE
  cache_status <- "not found"

  if (use_caching && file.exists(cache_file)) {
    # Check age of cache file
    cache_age_days <- as.numeric(difftime(Sys.time(), file.info(cache_file)$mtime, units = "days"))

    if (cache_age_days <= cache_max_age_days) {
      should_use_cache <- TRUE
      cache_status <- paste0("exists, age ", round(cache_age_days, 1), " days (< ", cache_max_age_days, " days) - using cache")
    } else {
      cache_status <- paste0("exists but stale, age ", round(cache_age_days, 1), " days (> ", cache_max_age_days, " days) - recomputing")
    }
  } else if (use_caching) {
    cache_status <- "not found - computing"
  } else {
    cache_status <- "cache disabled - computing"
  }

  # Log cache status
  cache_msg <- paste0("[Worker ", worker_id, "] Imputation ", i, " cache: ", cache_status)
  cat(paste0(Sys.time(), " - ", cache_msg, "\n"), file = worker_log_file, append = TRUE)

  if (should_use_cache) {
    cached_result <- readRDS(cache_file)
    weights <- cached_result$weights

@@

# Process each imputation sequentially
sequential_results <- lapply(
  1:n_imputations,
  function(i) {
    worker_id <- 1  # Single worker for sequential processing
    process_imputation(i, imputed_datasets, ps_formula, n_trees, cache_dir, use_cache, worker_id, log_dir, cache_max_age_days)
  }
)

@@

  # Log individual result summary in main log (details in worker log)
  if (res$cached) {
    log_message(paste0("Imputation ", res$imputation, ": Used cached result"))
  } else {
    log_message(paste0("Imputation ", res$imputation, ": Computed in ", res$time_mins, " minutes"))
  }
}

@@

# Cache usage summary
n_cached <- sum(progress_df$Cached)
n_computed <- sum(!progress_df$Cached)
cache_time_saved <- round(n_cached * mean(progress_df$Time_Minutes[!progress_df$Cached], na.rm = TRUE), 1)

log_message("=== Cache Summary ===")
log_message(paste0("Total imputations: ", n_imputations))
log_message(paste0("Used cache: ", n_cached, " (", round(100 * n_cached / n_imputations, 1), "%)"))
log_message(paste0("Newly computed: ", n_computed, " (", round(100 * n_computed / n_imputations, 1), "%)"))
if (n_computed > 0 && n_cached > 0) {
  log_message(paste0("Estimated time saved: ~", cache_time_saved, " minutes"))
}
log_message("=====================")
